Raw Traces

### 2023-05-17 Fish Data Analysis/Raw Traces Figure.qmd
Fixing 2021_10_08_17 Data

```{r}
library(gsignal)
library(tidyverse)
library(ggplot2)
library(ggpubr)
library(plotly)
```

@@

#unique(comp_data_all$Data_ID)

@@

example_data <- comp_data_all %>% filter(Data_ID == "2021_7_7_14") #%>% filter(Fish1 == "individual1")

smooth_data <- example_data %>% group_by(Fish1,Frame_Num) %>%
                               summarise(Fish1_X = mean(Fish1_X),
                                         Fish1_Y = mean(Fish1_Y),
                                         Fish1_Z = mean(Fish1_Z),
                                         Fish1_Speed = mean(Fish1_Speed),
                                         Fish1_Yaw_Heading = mean(Fish1_Yaw_Heading)) %>%
                               group_by(Fish1) %>%
                               mutate(Fish1_X_Smooth = supsmu_right_length_y(Frame_Num,Fish1_X),
                                      Fish1_Y_Smooth = supsmu_right_length_y(Frame_Num,Fish1_Y),
                                      Fish1_Z_Smooth = supsmu_right_length_y(Frame_Num,Fish1_Z),
                                      Fish1_Speed_Smooth = supsmu_right_length_y(Frame_Num,Fish1_Speed),
                                      Speed_Increasing_Smooth = ifelse(Fish1_Speed < lead(Fish1_Speed),1,0),
                                      Fish1_Yaw_Heading_Max_Unwrap = rad2deg(supsmu_right_length_y(Frame_Num,unwrap(deg2rad(Fish1_Yaw_Heading))))) %>%
                               ungroup()

@@

>>>>

```{r}
library(gsignal)
library(tidyverse)
library(ggplot2)
library(ggpubr)
library(plotly)
library(zoo)
```

@@

unique(comp_data_all$Data_ID)

@@

example_data <- comp_data_all %>% filter(Data_ID == "2021_10_8_27")

smooth_data <- example_data %>% group_by(Fish1,Frame_Num) %>%
                               summarise(Fish1_X = mean(Fish1_X),
                                         Fish1_Y = mean(Fish1_Y),
                                         Fish1_Z = mean(Fish1_Z),
                                         Fish1_Speed = mean(Fish1_Speed),
                                         Fish1_Yaw_Heading = mean(Fish1_Yaw_Heading)) %>%
                               group_by(Fish1) %>%
                               mutate(Fish1_X_Smooth = supsmu_right_length_y(Frame_Num,Fish1_X),
                                      Fish1_Y_Smooth = supsmu_right_length_y(Frame_Num,Fish1_Y),
                                      Fish1_Z_Smooth = supsmu_right_length_y(Frame_Num,Fish1_Z),
                                      Fish1_Speed_Smooth = supsmu_right_length_y(Frame_Num,Fish1_Speed),
                                      Speed_Increasing_Smooth = ifelse(Fish1_Speed < lead(Fish1_Speed),1,0),
                                      Fish1_Yaw_Heading_Max_Unwrap = rad2deg(supsmu_right_length_y(Frame_Num,unwrap(deg2rad(Fish1_Yaw_Heading))))) %>%
                               ungroup() %>% 
                               filter(Fish1_Z_Smooth >= -0.1 & Fish1_Z_Smooth <= 5)

@@

 Okay now we're going to try and replace all missing parts with a spline

"2021_7_7_19"  "2021_7_7_27"  "2021_10_8_27" "2021_7_7_16"  "2021_7_7_17"  "2021_7_7_14"  "2021_10_8_21" "2021_10_8_26" "2021_7_7_6"   "2021_10_8_15"

example_data_spline <- comp_data_all %>% filter(Data_ID == "2021_10_8_21")

spline_data <- example_data_spline %>% group_by(Fish1,Frame_Num) %>%
                               summarise(Fish1_X = mean(Fish1_X),
                                         Fish1_Y = mean(Fish1_Y),
                                         Fish1_Z = mean(Fish1_Z),
                                         Fish1_Speed = mean(Fish1_Speed),
                                         Fish1_Yaw_Heading = mean(Fish1_Yaw_Heading)) %>%
                               group_by(Fish1) %>%
                               mutate(Fish1_X_IB = ifelse(Fish1_Z >= -0.1 & Fish1_Z <= 5,Fish1_X,NA),
                                      Fish1_Y_IB = ifelse(Fish1_Z >= -0.1 & Fish1_Z <= 5,Fish1_Y,NA),
                                      Fish1_Z_IB = ifelse(Fish1_Z >= -0.1 & Fish1_Z <= 5,Fish1_Z,NA),
                                      Fish1_Speed_IB = ifelse(Fish1_Z >= -0.1 & Fish1_Z <= 5,Fish1_Speed,NA),
                                      Fish1_Heading_IB = ifelse(Fish1_Z >= -0.1 & Fish1_Z <= 5,Fish1_Yaw_Heading,NA)) %>%
                               mutate(Fish1_X_Spline = na.spline(Fish1_X_IB) + 0*na.approx(Fish1_X_IB, na.rm = FALSE),
                                      Fish1_Y_Spline = na.spline(Fish1_Y_IB) + 0*na.approx(Fish1_Y_IB, na.rm = FALSE),
                                      Fish1_Z_Spline = na.spline(Fish1_Z_IB) + 0*na.approx(Fish1_Z_IB, na.rm = FALSE),
                                      Fish1_Speed_Spline = na.spline(Fish1_Speed_IB) + 0*na.approx(Fish1_Speed_IB, na.rm = FALSE),
                                      Fish1_Heading_Spline = na.spline(Fish1_Heading_IB) + 0*na.approx(Fish1_Heading_IB, na.rm = FALSE))%>%
                               ungroup()

fig <- plot_ly() %>%
       add_trace(x = spline_data$Fish1_X_Spline, y = spline_data$Fish1_Y_Spline, z = spline_data$Fish1_Z_Spline,
               split = spline_data$Fish1, type = 'scatter3d', mode = 'lines', opacity = 1, line = list(width = 6),
               color = spline_data$Fish1,
               colors = c("#F8766D","#CD9600","#7CAE00","#00BE67","#00BFC4","#00A9FF","#C77CFF","#FF61CC")) %>%
       layout(showlegend = FALSE)
